### 2024-02-07 README.Rmd
move added logo

The following is a framework within which the `sfislands` functions could be used:

>>>>

The following is a framework within which the `sfislands` functions could be used.

The first group can be seen as pre-functions, designed to create a neighbourhood structure suitable for certain types of models.

Once a model has been fit (using `mgcv` in this case), the post-functions can be used to extract the predictions.
